sentiment-analysis

### 2016-08-09 eda/sentiment-analysis.Rmd
notes

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(jsonlite)
library(stringr)
library(ggplot2)
library(dplyr)
library(tidytext)
library(tm)
library(purrr)
source("../functions/PercentAccuracy.R")
source("../functions/MeanStar.R")
```

@@

```{r, eval = T}
# boxplot for each group
ggplot(review_scores) +
  geom_boxplot(aes(stars, sentiment, group = stars)) +
  labs(x = "Business Star Rating",
       y = "Mean Sentiment Score",
       title = "Mean Sentiment Score vs. Business Star Rating")
```

@@

```{r fig.height = 7, fig.width = 7}
summaries %>% 
  ggplot(aes(reviews, average_star, color = score)) +
  geom_point() +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1, hjust = 1) +
  scale_x_log10(limits = c(200, 100000), 
                breaks = c(1000, 10000), labels = c(1000, 10000)) +
  geom_hline(yintercept = mean(reviews$stars), color = "black", lty = 2) +
  scale_color_gradient2(low = "red", high = "blue", 
                        midpoint = 0, mid = "grey") +
  labs(x = "# of reviews",
       y = "Average Yelp Stars",
       color = "Valence Score") +
  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1))
```

@@

This is pretty informative, but I want to see these words plotted by their valence score and average Yelp rating to visualize if there's a positive correlation here between sentiment score and their star rating. 
```{r fig.height = 7}
summaries %>% 
  arrange(desc(reviews)) %>% 
  ggplot(aes(score, average_star)) +
  geom_point(aes(size = reviews)) +
  geom_text(aes(label = word), vjust = 1, hjust = 1, check_overlap = TRUE) +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Valence Score") +
  ylab("Average Yelp Stars") +
  labs(title = "Average Yelp Star Rating vs. Valence Score") +
  scale_x_continuous(limits = c(-5,6), breaks = seq(-5, 5, 2)) +
  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1)) +
  expand_limits(x = -6)
```

@@

```{r}
data.frame(
  x = factor(-5:5), 
  y = unlist(-5:5 %>% map(MeanStar))) %>% 
  filter(!is.nan(y)) %>% 
  ggplot(aes(x = x, y = y, fill = x)) +
  geom_bar(stat = "identity") +
  labs(x = "Valence Score",
       y = "Average Star Rating",
       fill = "Valence Score")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(jsonlite)
library(stringr)
library(ggplot2)
library(dplyr)
library(tidytext)
library(tm)
library(ggrepel)
library(purrr)
source("../functions/PercentAccuracy.R")
source("../functions/MeanStar.R")
```

@@

```{r, eval = T}
# boxplot for each group
# ggplot(review_scores, aes(star, sentiment)) +
#   geom_bar(stat = "identity")
# coloring too messy, histogram/bar graph doesn't capture whole picture
# want to see if some 1-star ratings have 5s and vice versa
# boxplot shows this with outliers
ggplot(review_scores) +
  geom_boxplot(aes(stars, sentiment, group = stars)) +
  labs(x = "Business Star Rating",
       y = "Mean Sentiment Score",
       title = "Mean Sentiment Score vs. Business Star Rating")
```

@@

```{r fig.height = 7, fig.width = 7}
# x scale log - graph messy otherwise
# ggrepel - too much text, unreadable 
# line color black and dotted = most visible
# color scheme most visible
# plot less points? not meaningful enough then
summaries %>% 
  ggplot(aes(reviews, average_star, color = score)) +
  geom_point() +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1, hjust = 1) +
  scale_x_log10(limits = c(200, 100000), 
                breaks = c(1000, 10000), labels = c(1000, 10000)) +
  geom_hline(yintercept = mean(reviews$stars), color = "black", lty = 2) +
  scale_color_gradient2(low = "red", high = "blue", 
                        midpoint = 0, mid = "grey") +
  labs(x = "# of reviews",
       y = "Average Yelp Stars",
       color = "Valence Score") +
  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1))
```

@@

This is pretty informative, but I want to see these words plotted by their valence score and average Yelp rating to visualize if there's a positive correlation here between sentiment score and their star rating. 
```{r fig.height = 7}
# boxplot again?
# see specific words and overall trend
# line doesn't fit that well but shows positive trend so best fit
summaries %>% 
  arrange(desc(reviews)) %>% 
  ggplot(aes(score, average_star)) +
  geom_point(aes(size = reviews)) +
  geom_text(aes(label = word), vjust = 1, hjust = 1, check_overlap = TRUE) +
  geom_smooth(method = "loess", se = FALSE) +
  xlab("Valence Score") +
  ylab("Average Yelp Stars") +
  labs(title = "Average Yelp Star Rating vs. Valence Score") +
  scale_x_continuous(limits = c(-5,6), breaks = seq(-5, 5, 2)) +
  scale_y_continuous(limits = c(1, 5), breaks = seq(1, 5, 1)) +
  expand_limits(x = -6)
```

@@

```{r}
# histogram complains
# bar graph good (Y)
data.frame(
  x = factor(-5:5), 
  y = unlist(-5:5 %>% map(MeanStar))) %>% 
  filter(!is.nan(y)) %>% 
  ggplot(aes(x = x, y = y, fill = x)) +
  geom_bar(stat = "identity") +
  labs(x = "Valence Score",
       y = "Average Star Rating",
       fill = "Valence Score")
```
